Temporal and Spatial Analysis of Hate Crimes in Toronto

### 2024-09-25 paper/paper.qmd
data section editted and unnecessary datasets are dropped

The data section will introduced the detail of the data set used in this research. The variables as well as the cleaning process will be discussed in this section. The result section will focus on the findings and the visualization of the analysis. The discussion session talks about the limitation of this research and potential error caused by research design or the natural form of data. lastly, the conclusion part raps up the discovers and summarizes all the findings into a short paragraph.

@@

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

@@

# Results

@@

# Discussion

@@

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

>>>>

The data section will introduced the detail of the data set used in this research in @sec-data -- Data. The variables as well as the cleaning process will be discussed in this section. The result section @sec-results will focus on the findings and the visualization of the analysis. The discussion session @sec-discussion talks about the limitation of this research and potential error caused by research design or the natural form of data. lastly, the conclusion part raps up the discovers and summarizes all the findings into a short paragraph.

@@

## Measurement and packages {#sec-measurement and packages}
The Data set used in the analysis is gathered from Open Data Toronto through the Open Data Toronto [@opendatatoronto] and used the statistical software R [@citeR] for importing data, data cleaning and testing data. The data source "Crime Data" is used from [@open-data-set] collected from Toronto Police starting from 2018 to the end of 2023. It includes both temporal and spatial attributes. Other packages were used for analyzing the data such as ggplot [@ggplot2], tidyverse [@tidyverse], lubridate [@lubridate], dplyr [@dplyr],tinytex [@tinytex].

Data contains around 1400 observations and contains the occurrence date and specific time where the incident happened and the date reported to the police. The reason for the hate crime is categorized as race bias, religion bias and sexual orientation bias etc. The motive for 
committing a crime, the illegal activity and the neighborhood where the crime occurred are documented by the police throughout the years. Furthermore, the type of location  such as park, apartment and school are documented to form the detailed data set and is named "Hate Crime".

## Data cleaning {#sec-data cleaning}

After observing the data, some observations were dropped due to missing values in location type meaning the recorder had a hard time describing the location characteristics. Therefore, these observations were dropped out of the cleaned data set and will not be included in further data analysis. Date is critical in our data investigation, observations where the reported time is before occurrence time is dropped to assure data validity. Since the data set is from Open Data Toronto the quality of the data is decent. Further cleaning process is unnecessary due to origin high quality of data set .

## Observation

@@

# Results {#sec-results}

@@

# Discussion {#sec-discussion}

@@

@@
